$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-12-14 paper/appendix.tex
Adapt to LLNCS style

\begin{nilemma}
  Translating from de Bruijn indices to names via $\func{toRaw}$ results in a well-scoped process.
\end{nilemma}

\begin{nilemma}
  Translating from de Bruijn indices to names via $\func{toRaw}$ results in a process that follows the \emph{Barendregt convention}.
\end{nilemma}

\begin{nilemma}
  Translating from de Bruijn indices to names and back via $\func{fromRaw} \circ \func{toRaw}$ results in the same process modulo internal variable name hints.
\end{nilemma}

\begin{nilemma}
  Translating from names to de Bruijn indices and back via $\func{toRaw} \circ \func{fromRaw}$ results in the same process modulo $\alpha$-conversion.
\end{nilemma}

@@

\section{Definitions}
\label{app:definitions}

\begin{nidefinition}
  A variable $i$ is unused in $P$ ($\Unused_i \; P$) if it appears in none of its inputs and none of its outputs.

  \begin{mathpar}
    \datatype
    {i : \Var_n \\ P : \Process_n}
    {\Unused_i \; P}
    \; \textsc{Unused}

    \inferrule
    { }
    {\Unused_i \; \PO}

    \inferrule
    {\Unused_{\suc i} \; P}
    {\Unused_i \; \new{}P}

    \inferrule
    {\Unused_i \; P \\ \Unused_i \; Q}
    {\Unused_i \; \comp{P}{Q}}

    \inferrule
    {i \type{\not\equiv} x \\ \Unused_{\suc i} \; P}
    {\Unused_i \; \recv{x}{} P}

    \inferrule
    {i \type{\not\equiv} x \\ i \type{\not\equiv} y \\ \Unused_i \; P}
    {\Unused_i \; \send{x}{y} P}
  \end{mathpar}

  The type $i \type{\not\equiv} x$ unfolds to the negation of propositional equality on \textsc{Var}, i.e. $i \type{\equiv} x \to \type{\bot}$.
\end{nidefinition}

@@

\begin{nitheorem}[Generalised substitution]
  \label{thm:subst-generalization1}
  Let process $P$ be well-typed in $\types{\gamma}{\Gamma_i}{P}{\Psi_i}$.
  The substituted variable $i$ is capable of $m$ in $\Gamma_i$, and capable of $n$ in $\Psi_i$.
  Substitution will take these usages $m$ and $n$ away from $i$ and transfer them to the variable $j$ we are substituting for.
  In other words, there must exist some $\Gamma$, $\Psi$, $\Gamma_j$ and $\Psi_j$ such that:
  \begin{multicols}{2}
  \begin{itemize}
    \item $\contains{\gamma}{\Gamma_i}{i}{t}{m}{\Gamma}$
    \item $\contains{\gamma}{\Gamma_j}{j}{t}{m}{\Gamma}$
    \item $\contains{\gamma}{\Psi_i}{i}{t}{n}{\Psi}$
    \item $\contains{\gamma}{\Psi_j}{j}{t}{n}{\Psi}$
  \end{itemize}
  \end{multicols}
  Let $\Gamma$ and $\Psi$ be related such that $\opctx{\Gamma}{\Delta}{\Psi}$ for some $\Delta$.
  Let $\Delta$ have a usage annotation $\lz$ at position $i$, so that all consumption from $m$ to $n$ must happen in $P$.
  Then substituting $i$ to $j$ in $P$ will be well-typed in $\types{\gamma}{\Gamma_j}{\subst{P}{j}{i}}{\Psi_j}$.
  Refer to \autoref{fig:subst} for a diagramatic representation.
\end{nitheorem}

>>>>

\begin{lemma}
  Translating from de Bruijn indices to names via $\func{toRaw}$ results in a well-scoped process.
\end{lemma}

\begin{lemma}
  Translating from de Bruijn indices to names via $\func{toRaw}$ results in a process that follows the \emph{Barendregt convention}.
\end{lemma}

\begin{lemma}
  Translating from de Bruijn indices to names and back via $\func{fromRaw} \circ \func{toRaw}$ results in the same process modulo internal variable name hints.
\end{lemma}

\begin{lemma}
  Translating from names to de Bruijn indices and back via $\func{toRaw} \circ \func{fromRaw}$ results in the same process modulo $\alpha$-conversion.
\end{lemma}

@@

@@

\begin{theorem}[Generalised substitution]
  \label{thm:subst-generalization1}
  Let process $P$ be well-typed in $\types{\gamma}{\Gamma_i}{P}{\Psi_i}$.
  The substituted variable $i$ is capable of $m$ in $\Gamma_i$, and capable of $n$ in $\Psi_i$.
  Substitution will take these usages $m$ and $n$ away from $i$ and transfer them to the variable $j$ we are substituting for.
  In other words, there must exist some $\Gamma$, $\Psi$, $\Gamma_j$ and $\Psi_j$ such that:
  \begin{multicols}{2}
  \begin{itemize}
    \item $\contains{\gamma}{\Gamma_i}{i}{t}{m}{\Gamma}$
    \item $\contains{\gamma}{\Gamma_j}{j}{t}{m}{\Gamma}$
    \item $\contains{\gamma}{\Psi_i}{i}{t}{n}{\Psi}$
    \item $\contains{\gamma}{\Psi_j}{j}{t}{n}{\Psi}$
  \end{itemize}
  \end{multicols}
  Let $\Gamma$ and $\Psi$ be related such that $\opctx{\Gamma}{\Delta}{\Psi}$ for some $\Delta$.
  Let $\Delta$ have a usage annotation $\lz$ at position $i$, so that all consumption from $m$ to $n$ must happen in $P$.
  Then substituting $i$ to $j$ in $P$ will be well-typed in $\types{\gamma}{\Gamma_j}{\subst{P}{j}{i}}{\Psi_j}$.
  Refer to \autoref{fig:subst} for a diagramatic representation.
\end{theorem}
